% Created 2021-11-30 Tue 17:07
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Alex Menendez, Stanley C Kemp}
\date{\today}
\title{Design Document}
\hypersetup{
 pdfauthor={Alex Menendez, Stanley C Kemp},
 pdftitle={Design Document},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.2 (Org mode 9.4.4)}, 
 pdflang={English}}
\begin{document}

\maketitle

\section{What Are We Going to Do?}
\label{sec:org6ddc32c}
We are going to create a game about rotating/moving an object in
order to fit it into a moving pane. The panes come faster as
difficulty increases, and the holes get smaller (but not impossible
to fit into ☺)

\subsection{Controls}
\label{sec:orgac249ab}

\subsubsection{Scheme 1}
\label{sec:orgeab2c53}
\begin{itemize}
\item Q, E --- rotate counter/clockwise around depth
\item W, A, S, D --- standard movement controls
\item <, > --- rotate around height
\end{itemize}

\subsubsection{Scheme 2}
\label{sec:org9031708}
\begin{itemize}
\item Arrow keys --- move shape
\item E, D --- rotate around depth
\item W, S --- rotate around width
\item Q, A --- rotate around height
\end{itemize}
\section{How Are We Going to Do It?}
\label{sec:org0b47907}
\subsection{How are we going to generate the shapes?}
\label{sec:orgdf8c868}
Good question. The plan is to model a single shape at first in order
to test the abilities of our program. 
\subsection{How are we going to generate the holes?}
\label{sec:orgf6ff5df}
Using subtractive geometry. First, we will generate a silhouette of
the 3D shape that the user controls from a random angle.

Then, subtract the silhouette in a random place in a vector rectangle,
hollow out some more according to difficulty. Then extrude the rectangle
to get the hole.

\subsection{How is the difficulty going to increase?}
\label{sec:org662029e}
\end{document}
